### 2019-08-19 chapter_02_open_science.tex
Typos

\item \textbf{Lively, and thus, complicated ecosystem of packages.} For many
	applications, the standard library is insufficient and external
	packages are needed. Sometimes there are multiple options and the
	user/developer has to make choices regarding the tools to use.
	Especially for the beginners who are not used to the open-source realm,
	it can be confusing prospect to make good technological choices; but
	this can be solved through proper guidance and training.
	Of course, such an abundance of projects can also be seen as an advantage.

>>>>

\item \textbf{Lively, and thus, complicated ecosystem of packages.} For many
	applications, the standard library is insufficient and external
	packages are needed. Sometimes there are multiple options and the
	user/developer has to make choices regarding the tools to use.
	Especially for the beginners who are not used to the open-source realm,
	it can be a confusing prospect to make good technological choices; but
	this can be solved through proper guidance and training.
	Of course, such an abundance of projects can also be seen as an advantage.
